---
title: "Auxiliary functions"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
fig_caption: yes
bibliography: CITES.bib
link-citations: yes
vignette: >
  %\VignetteIndexEntry{Auxyliary functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
<style>
body {
text-align: justify}
</style>

```{r setup, include = FALSE}
library(mpxtractor)
library(dplyr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Overview 
As a part of `mpxtractor` some functions that are present in `wrangling functions` or `plotting functions` can be used independently. Here are explained some auxilary functions that can be used separately.

## 1. format_time()
This fuction transform the attribute **Time** from hh:mm:ss to time in hours.

```{r echo=FALSE}
data(df_spectramax_outdata_1)
data_spectra <- head(df_spectramax_outdata_1)

htmlTable::htmlTable(as.matrix(data_spectra), caption = "**Table 1:** Shows a capture of the data with the time in hh:mm:ss format.")
```

Once the dataframe is created is passed to the function and the time is 
formatted.
In the case of multiscanGO files this function return the same dataframe given as input. In this case a one warning is shown.

```{r}
# Time in hours
df_hh <- mpxtractor::format_time(data_spectra)
# Time in minutes
df_mm <- mpxtractor::format_time(data_spectra, time_format = "minutes")
```

```{r echo=FALSE}
knitr::kable(list(df_hh, df_mm), caption = "**Table 2:** Shows a capture of
the data with the time in hours (left) and in minutes (right).")
```


## 2. compute_growth_rates()
This function can be handy when one dataset is avilable and we want to do a quick calculation of growth curves. 
### Example:
In this example the data is transform in the same way used in the example in 
the vignette `plotting_functions`. The background is subtracted followed by the log transform.

### 2.1 Read and load the data
In this example because is an output file from SpectraMax we use `read_spectramax_data()`.

```{r}
# Get the file path 
file_path_sp <- system.file(
  "extdata",
  "test_gr_spectramax.txt",
  package = "mpxtractor"
)
# Extract the data stored in the files into a data frame using proper wrangling function
df_sp <- mpxtractor::read_spectramax_data(
  file = file_path_sp
)

head(df_sp)
```

### 2.2 Background correction and log transform
Here we correct by the minimun measurement followed by the logarithmic transformation.

```{r}
# Get the minimun measurement for each well
df <- df_sp %>%
  group_by(Wells) %>%
  mutate(min_measurement = min(Measurement))

# Subtract the minimun to each measurement
df_tmp <- df %>%
  mutate(bg_corrected = Measurement - min_measurement)

# Apply log transform and clean the dataframe
df_corrected <- df_tmp %>%
  mutate(Measurement = log(bg_corrected)) %>%
  select(-c(min_measurement, bg_corrected))

head(df_corrected)  
```

### 2.3 Compute the growth rates.
Here the the function `compute_growth_rates()` is used. 
Some insights about this function:

  - The argument **var_gr** is the attribute used to calculate the growth rates.
  - The growth rates are calculated using *sgolayfilt()* from the package @signal, this function is taking: the first derivative, the windowlength given as a parameter in `compute_growth_rates()` and using as a time scaling factor the time points used in the experiment. 
  - The function *sgolayfilt()* is not taking into account the time.
  - The growth rates are calculated by wells.
  
  
Is very important to note that the difference between time points must be equal for all them. Otherwise the time series is not complete.

```{r}
 df_gr_data <- mpxtractor::compute_growth_rates(
   df_data = df_corrected,
   var_gr = "Measurement",
 ws = "2hs"
)
head(df_gr_data)
```


## References



