---
title: "Data wrangling functions of `mpxtractor` package"
author: "Martin Banchero"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Main functions in `mpxtractor`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
<style>
body {
text-align: justify}
</style>

```{r, include = FALSE}
library(mipledxtractor)
library(kableExtra)
knitr::opts_chunk$set(collapse = TRUE,comment = "#>")
```

## Overview
The main function of `mpxtractor` is to provide a simple method that is able to 
process raw data from micro plate readers and generate a tidy data frame. This is
a critical point in several research lines performing experiments using micro plate 
reader machines because of the time that takes to clean and sort the raw data into 
a tidy format. 
This package main contribution is orientated to save time and get fast into data 
analysis.
In the following sections the main functions of data wrangling of `mpxtractor` 
are described.

## 1. Wrangling functions
The `mpxtractor` contain one function for each type of micro plate reader machine. This functions are, *read_spectramax_data()*, *read_multiscango_data()*, *read_fluorstar_data()*. In addition to this
the function *read_multiple_files()* is used to combine more than one output file into one tidy
data frame. In the following section each of this functions are explained.

### 1.1 read_spectramax_data()
This function take as argument one file with ".txt" extension. Also is a "\\t" separated
file. 
Below is shown a toy example about how to use this function.

```{r}
file_path <- system.file("extdata", "test_spectramax_data_1.txt", package = "mpxtractor")

data_spectramax <- mpxtractor::read_spectramax_data(file = file_path)

head(data_spectramax)
```

### 1.2 read_multiscango_data()

```{r}
file_path <- system.file("extdata", "test_multiscango_data_1.txt", package = "mpxtractor")
data_multiscan <- mpxtractor::read_multiscango_data(file = file_path)
head(data_multiscan)
```



### 1.3 read_fluorstar_data()

```{r}
file_path <- system.file("extdata", "test_fluorstar_fluorescence_data.txt", package = "mpxtractor")
data_fluorstar <- mpxtractor::read_fluorstar_data(file = file_path)
head(data_fluorstar)

```


### 1.4 read_multiple_files()

```{r}
file_path <- system.file("extdata", 
                         c("test_spectramax_data_1.txt","test_spectramax_data_2.tx"), 
                         package = "mpxtractor")

data_multiple_spectramax <- mpxtractor::read_multiple_data_files(
                                                      reader_type = "spectramax",
                                                      filesname = file_path)
head(data_multiple_spectramax)
tail(data_multiple_spectramax)
```


```{r}
tail(data_multiple_spectramax)
```




