---
title: "Data wrangling functions of `mpxtractor` package"
author: "Martin Banchero"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Main functions in `mpxtractor`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(mipledxtractor)
library(kableExtra)
knitr::opts_chunk$set(collapse = TRUE,comment = "#>")
```

## Overview
The main function of `mpxtractor` is to provide a simple method that is able to represent
the data of a microplate reader output file into a tidy data frame. This is a critical point in severals reasearch lines related to molecular biolgy. This package main contribution is orientated to save time and get fast into data analysis.
In the following sections the main functions of data wrangling of `mpxtractor` are described.
In addition to the data wrangling functions, `mpxtractor` provide functions to deal with
layout files like *read_layout_file()* and *combine_data_with_layout()* which generate a tidy
dataframe between the raw_data and the information present in the layout files.

## 1. Wrangling functions
The `mpxtractor` contain one function for each type of microplate reader machine. This functions are, *read_spectramax_data()*, *read_multiscango_data()*, *read_fluorstar_data()*. In addition to this
the function *read_multiple_files()* is used to combine more than one output file into one tidy
dataframe. In the following section each of this functions are explained.

### 1.1 read_spectramax_data()
This function take as argument one file with ".txt" extension. Also is a "\\t" separated
file. 

```{r}
file_path <- system.file("extdata", "spectraMax_1stplate.txt", package = "mpxtractor")
data_spectramax <- mpxtractor::read_spectramax_data(file = file_path)
head(data_spectramax)
```

### 1.2 read_multiscango_data()

```{r}
file_path <- system.file("extdata", "multiscanGO_1streading.txt", package = "mpxtractor")
data_multiscan <- mpxtractor::read_multiscango_data(file = file_path)
head(data_multiscan)
```



### 1.3 read_fluorstar_data()

```{r}
file_path <- system.file("extdata", "fluorstar_milkjuice_FL.txt", package = "mpxtractor")
data_fluorstar <- mpxtractor::read_fluorstar_data(file = file_path)
head(data_fluorstar)

```


### 1.4 read_multiple_files()

```{r}
file_path <- system.file("extdata", 
                         c("spectraMax_1stplate.txt","spectraMax_2ndplate.txt"), 
                         package = "mpxtractor")

data_multiple_spectramax <- mpxtractor::read_multiple_data_files(
                                                      reader_type = "spectramax",
                                                      filesname = file_path)
head(data_multiple_spectramax)
```


```{r}
tail(data_multiple_spectramax)
```

## 2. Deal with layout files functions
### 2.1 read_layout_files()
```{r}


```

### 2.2 combine_data_with_layout()

```{r}

```





