---
title: "Layout files process functions"
author: "Martin Banchero"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(mipledxtractor)
library(kableExtra)
knitr::opts_chunk$set(collapse = TRUE,comment = "#>")
```

## Overview

## 1. Deal with layout files functions
The `mpxtractor` contain one function for each type of microplate reader machine. This functions are, *read_spectramax_data()*, *read_multiscango_data()*, *read_fluorstar_data()*. In addition to this
the function *read_multiple_files()* is used to combine more than one output file into one tidy
dataframe. In the following section each of this functions are explained.
In addition to the data wrangling functions, `mpxtractor` provide functions to deal with
layout files like *read_layout_file()* and *combine_data_with_layout()* which generate a tidy
data frame between the raw_data and the information present in the layout files.


### 2.1 read_layout_files()
```{r}


```

### 2.2 combine_data_with_layout()
```{r}

```

