---
title: "Read layout files with `mpxtractor` package"
author: "Martin Banchero"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Read layout files in `mpxtractor`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(mipledxtractor)
library(kableExtra)
knitr::opts_chunk$set(collapse = TRUE,comment = "#>")
```

### Overview
This function of `mpxtractor` is to add the layout files to the tidy data obtained by one of the main functions.

### 1. read_layout_files()
#### 1.1 Generate data argument
First the tibble generated by one of the main functions is needed. This is a key step because
*read_layout_file()* take as argument the measured data. Then the function add the layout to file
as new columns.

```{r}
file_path_spec_data <- system.file("extdata", "spectraMax_1stplate.txt", package = "mpxtractor")
data_spectramax <- mpxtractor::read_spectramax_data(file = file_path_spec_data)
head(data_spectramax)
```

#### 1.2 Explicit arguments
The function `read_layout_file()` takes another arguments beside the data. The type of machine where the data is produced, the *reader_type* argument and the files. This can be one file or multiple files.

```{r}
file_path_layout <- system.file("extdata", "spectraMax_layout_plate1.csv", package = "mpxtractor")

# Data is store as a tibble
data_layout <- mpxtractor::read_layout_files(data_spectramax, reader_type = "spectramax", layout_files = file_path_layout)
head(data_layout)
```
