---
title: "Main functions of `mpxtractor` package"
author: "Martin Banchero"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Main function in `mpxtractor`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(mipledxtractor)
library(kableExtra)
knitr::opts_chunk$set(collapse = TRUE,comment = "#>")
```

## Overview
The main function of `mpxtractor` is to provide a simple method that is able to represent
the data staore in an output file of a microplate reader into a tidy data frame. This is a critical point in severals reasearch lines link to molecular biolgy. This package main contribution is orientated to save time and get fast into data analysis.
In the following sections the main functions of `mpxtractor` are described.

## 1. Main functions
The `mpxtractor` contain one function for each type of microplate reader machine. This functions are, *read_spectraMax_data()*, *read_multiscanGO_data()* and *read_fluorStar_data()*, in the following section each of this functions are explained.

### 1.1 read_spectraMax_data()
This function take as argument one file with ".txt" extension. Also is a "\\t" separated
file. 

```{r}
#file <- ("~/Master_VU_Mayor/spectraMAx/data/20190701_growthrates_mg1363_pt2_smA_1stplate.txt")

head(table)
```

### 1.2 read_multiscanGO_data()




### 1.3 read_fluorStar_data()






