---
title: "Brief introduction to `mpxtractor`"
author: "Martin Banchero"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
fig_caption: yes
bibliography: CITES.bib
link-citations: yes
vignette: >
  %\VignetteIndexEntry{Brief introduction to `mpxtractor`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
<style>
body {
text-align: justify}
</style>

```{r setup, include = FALSE}
library(mpxtractor)
library(dplyr)
knitr::opts_chunk$set(fig.width = 7, fig.height = 5 ,collapse = TRUE, comment = "#>")
```


## Advantages of use mpxtractor
It is well known for anyone performing experiments that involved microplate readers
that the analysis of the raw data can be tedious and time consuming. Several 
of this microplate reader machines include softwares to aliviate this problem but
many times are not very handy. Although several good R packages exists many of them are design to solve specific problems lossing generability. For example some features from @plater were used to build `mpxtractor`.  To clarify, `mpxtractor` can process
raw data from three different microplate reader machines, SpectraMax, MultiscanGO and
FluorStar.

For the reasons mentioned above is why `mpxtractor` can help to reduce the time to process the raw data into tidy dataframes, combine layout files
with tidy data. Also, `mpxtractor` provides features to visualize growth curves 
and layout files over a microplate frame. The latter can be printed to be use in
the lab during the set ups of experiments. 


## Features of `mpxtractor` 
This package is divided by two sets of functions

1. Function to wrangling the data in raw files, this functions are explained in 
detail in vignette `wrangling_and_layout_functions` along side with some examples.

2. Functions to plot layout files and growth curves, the vignette `plotting_functions` exlain how they work and some details.


## Example
Lets suppose we want to perform an experiment with some bacterias. The first step 
is design the experiment. 

As the first step we can prepare the layout file and see
the distribution of our samples over the plate. In this case we can plot the layout file and check the diagram. For example to avoid edge effects due to temperature, evaporation, etc. The wells around the perimeter of the plate might be more sensitive to this effects, visualizing the layout desing over the microplate is more easy to chaeck wether the control or the samples are well positioned in the plate. Here the function `plot_layout_file()` can be used to
get an overview of the design.

```{r}
#get the path to file
file <- system.file(
  "extdata", "test_multiscanGO_layout1.csv",
  package = "mpxtractor"
)

mpxtractor::plot_layout_file(file, var_shape = "Basic", var_colour = "presugar", plate_title = "Multiscango")
```











