---
title: "Plotting functions"
author: "Martin Banchero"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
fig_caption: yes
bibliography: REFERENCES.bib
link-citations: yes
vignette: >
  %\VignetteIndexEntry{plotting_functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
<style>
body {
text-align: justify}
</style>

```{r, include = FALSE}
library(mpxtractor)
knitr::opts_chunk$set(fig.width = 7.2, fig.height = 5 ,collapse = TRUE, 
                      comment = "#>")
```

## Overview
This section explains two functions of `mpxtractor` to visualize the layout files  and the growth rates over a microplate representation. This functions are 
**plot_layout_file()** and **plot_gr_microplate()** respectively.
In the next sections both functions are explained and one example is provided for 
each function.

## 1. **plot_layout_file()** 
This function can take several arguments in order to improve the flexiblity of the function. The first argument is a .csv layout with the proper format(check .csv files in folder inst/extdata). The following arguments are the features that are required to identify the different conditions, like var_shape and var_colour. 

**Important remarks:** Note that in order to obtain a better visualization the argument
var_shape should should contain less than six diferent factors. While var_color has no limits.

The implementation was taken from @plot_microtiter_plate with some minor
modifications.

```{r, fig.show='hold', fig.cap="Figure 1: Representation over a microplate frame of two different conditions, condition and strain. Note that strain contain less than 6 factors."}
file_path_fl <- system.file("extdata", "test_spectraMax_layout_1.csv", package = "mpxtractor")

mpxtractor::plot_layout_file(file = file_path_fl, var_shape = "strain", var_colour = "condition")

```



## 2. **plot_gr_microplate()**

## References
