---
title: "Data wrangling functions"
author: "Martin Banchero"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
bibliography: CITES.bib
link-citations: yes
vignette: >
  %\VignetteIndexEntry{wrangling_and_layout_functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
<style>
body {
text-align: justify}
</style>

```{r, include = FALSE}
library(mpxtractor)
knitr::opts_chunk$set(collapse = TRUE,comment = "#>")
```

## Overview
The `mpxtractor` contain one function for each type of micro plate reader machine. Each  of this functions are disgn to wrangle the raw data produced for this machines, this are: *read_spectramax_data()*, *read_multiscango_data()* and *read_fluorstar_data()*. In addition to this the function *read_multiple_files()* is used to combine more than one output file into one tidy data frame. 
To simplify the number of tasks that the user have to apply before load the
data in R, all this wrangling functions receive a file with .txt extension. This allows
to  avoid different issues realted to file formats, like .csv, .xlsx or versions. This is simplified by using only .txt files.

In addition to data wrangling functions, `mpxtractor` provide functions to deal with
layout files like *read_layout_file()* and *combine_data_with_layout()* which generate a tidy data frame that combine the output of one wrangling function with the layout files.


## 1. Wrangling functions
In this section is described each of the wrangling functions with examples using
test data.
 
### 1.1 read_spectramax_data()
This function is specific to read output files (.txt) produced by spectraMax readers.
Recive one raw file and generate a tibble dataframe.
The file is the path to a proper .txt file formatted by the spectraMax machine.
The returned tibble data frame show four columns. The first column is
"Wells" this containe the names for each well (A01, A02..). The second column
represent "Time" at wich the measurements were done, the format is in hh:mm:ss.
The third column is "Temperature", this is the temperature at which the
experiment was performed. The fourth column contain the measured values.

Below is shown a toy example about how to use this function. Note that measurement
represent the values of OD600 in this case.

```{r}
file_path <- system.file("extdata", "test_spectramax_data_1.txt", package = "mpxtractor")

data_spectramax <- mpxtractor::read_spectramax_data(file = file_path)

head(data_spectramax)
```

### 1.2 read_multiscango_data()
This function is specific to read output files (.txt) produced by multiscanGO readers.
Recive one raw file and generate a tibble dataframe and takes a time point which is given as argument.
The file is the path to a proper .txt file formatted by the multiscanGO machine.
The returned tibble data frame show four columns. The first column is
"Wells" this contain the names for each well (A01, A02..). The second column
represent "Time", this column is generated using the argument `time_point`, the third column is "Reading", shows the number of reading, and the fourth is "Measurement", this is the value measured for each "Reading".

**Important:** The time point given as an argument generates the time series, is 
very important to know the time between readings to use it to generate the attribute
`Time` in the tidy data frame.

Below is shown a toy example about how to use this function.

```{r}
file_path <- system.file("extdata", "test_multiscango_data_1.txt", package = "mpxtractor")
data_multiscan <- mpxtractor::read_multiscango_data(file = file_path, time_point = "2.5 min" )
head(data_multiscan)
```



### 1.3 read_fluorstar_data()
This function is specific to read output files (.txt) produced by fluorStar readers.
Recive one raw file and generate a tibble dataframe.
The file is the path to a proper .txt file formatted by the fluorStar machine.
The first column is "Wells" this containe the names for each well (A01, A02..). The second column represent "Sample" which identified the wells, this part of the standard output
of fluorStar machines.
The third column is "Time", that represents the timestep at which the machine measures. The fourth column contain the measured values. Depending on the experiment, this can be fluorescence, absorbance between others.

Below is shown a toy example about how to use this function. Note that in this example
fluorescence was measured.

```{r}
file_path <- system.file("extdata", "test_fluorstar_fluorescence_data.txt", package = "mpxtractor")
data_fluorstar <- mpxtractor::read_fluorstar_data(file = file_path)
head(data_fluorstar)
```


### 1.4 read_multiple_files()


```{r}

file_path <- system.file("extdata", c("test_spectramax_data_1.txt", "test_spectramax_data_2.txt"),
  package = "mpxtractor", mustWork = TRUE
)

data_multiple_spectramax <- mpxtractor::read_multiple_data_files(
  reader_type = "spectramax", filesname = file_path, plate_names = c("plate_1", "plate_2")
)

head(data_multiple_spectramax)
tail(data_multiple_spectramax)
```

## 2. Functions to read layout files
In this section are described the functions to extract information from the experimental design into a dataframe. Also, combine this information with tidy dataframes generated by the wrangling functions.

### 2.1 read_layout_files()
This function recive a layout file properly formatted. To get a better understanding of "properly formatted" check the files with .csv extension in "/inst/extdata".
This function is similar to the function read_plate() from `plater` package @plater  with some modifications.
The first column is "Wells" this contain the names for each well (A01, A02..). The rest of the attributes represent the different conditions.

```{r}
file_path <- system.file("extdata", "test_spectraMax_layout_1.csv", package = "mpxtractor")
df_layout_data <- mpxtractor::read_layout_file(file = file_path)
head(df_layout_data)
```

### 2.2 combine_data_with_layout()
This function recive as argument a dataframe (data) which is given for
one of the functions(read_spectramax_data, read_multiscango_data,
read_fluorstar_data). Also, the type of machine used and the path to the layout file has to be specified. 
Note that more than one layout file can be given.

```{r}
# generate data
file_path <- system.file("extdata", "test_spectramax_data_1.txt", package = "mpxtractor")
data_spectramax <- mpxtractor::read_spectramax_data(file = file_path)

# path to layout file
layout_file_path <- system.file("extdata", "test_spectraMax_layout_1.csv", package = "mpxtractor")

# Use combine_data_with_layout()
data_layout <- mpxtractor::combine_data_with_layout(
  data_multiple_spectramax, 
  reader_type = "spectramax",
  layout_files = layout_file_path
  )

# Now data is combined
head(data_layout)
tail(data_layout)
```


## References



